\chapter{Introduction}\label{chap1}


%##########################################

\vspace{2in}
\begin{center}
	\textbf{\large "Be A Part OF The Solution Not Part OF The Pollution"}
\end{center}


\newpage

Air is one of the essential elements of man’s surroundings. The earth’s atmosphere is full of air which contains gases such as Nitrogen, Oxygen, Carbon Monoxide and traces of some rare elements. Humans need an atmosphere of air that is free from contaminants. This is very crucial for human life and health. Any change in the natural composition of air may cause grave harm to life forms on earth. Air pollution is the presence of one or more contaminants in the atmosphere such as gases in a quantity that can harm humans, animals and plant . Air pollutants are measured in Parts per Million (ppm) or ug/m3. Primary pollutants are released directly into the atmosphere. Secondary pollutants are produced when the primary pollutant reacts with other atmospheric chemicals . Air quality affects public health. The effect of air pollution ranges from difficulty in breathing, coughing, aggravation of asthma and emphysema. Polluted air can also impair visibility. Air pollution is accountable for the death of 7 million persons worldwide each year or one in eight premature deaths yearly . Almost 570,000 children under the age of five die every year from respiratory infection linked to indoor/outdoor pollution and second-hand smoke. Children exposed to air pollution have an elevated risk of developing chronic respiratory problems such as asthma. In the monitoring of air pollution, several researchers worldwide have developed models to monitor many of the pollution gases such as Sulphur Dioxide (SO2), Carbon Monoxide (CO), Carbon Dioxide (CO2), Nitrogen Oxides (NO) etc. This thesis project focuses on the design and implementation of a smart air pollutant monitoring system. It discusses how the level of pollutants in the air can be monitored using a gas sensors, Raspberry Pi 4 \& Arduino UNO micro-controller. The main objective of this project is to design a smart air pollution monitoring system that can monitor, analyse and log data about air quality to a remote server, keep the data up to date over the internet and predict weather forecast of next few days based on past data.



%########################################################
\section{Outline of the report}
This report is organised around three main parts. 

{\bf Chapter~\ref{chap1}} Introduction to the project 

{\bf Chapter~\ref{chap2}} Describes literature review
    
{\bf Chapter~\ref{chap3}} Describes system design \& methodology of the project

{\bf Chapter~\ref{chap4}} Describes implementation \& testing of project

{\bf Chapter~\ref{chap5}} Conclusion

\section{Problem Statement}
The aim of this thesis project is to fulfill the following goals.

\begin{enumerate}
\item Create a system which will monitor the quality of air of our environment.
\item Collect information about the air pollution level after every certain period.
\item Content of different gases present in air or area around us.
\item To collect information about the air pollution level after every certain period.
\item Sense how much amount of gasses are present in air and display it in real time on smartphone.
\item Send the information of current air pollution level and weather forecast of next upcoming days to user smartphone.
\end{enumerate}

\section{Gantt Chart}

For proper completion of any work, there is need of a proper plan and the division of the work into small time frames. I divided my work according to the following Gantt Chart.

\begin{table}[!ht]
\centering
\begin{tabular}{ |p{4cm}|p{4cm}|p{4cm}|  }
\hline
\multicolumn{3}{|c|}{Air Pollution Detector} \\
\hline
20 Jan - 20 Feb  &  21 Feb - 12 April  &  05 April - 20 April  \\
\hline
& & \\
Planning, Setup and Literature Review& & \\
& & \\
&Designing and Implementation & \\
& & \\
& & Testing and Report-Writing  \\
& & \\
\hline
\end{tabular}
\caption{\label{ganthchart}Gantt chart}
\end{table}

\section{Internet of Things(IOT)}

Internet of Things (IOT) is a network of devices that connect directly with each other to capture and share data through a secure service layer that connects to a central command and control server in the cloud. The closure look suggest that the way people collect, record and analyze data not just in health care but in every industry today. The idea of devices connecting directly with each other is basically called Internet of Things.

The Internet of Things also called the Internet of Objects, refers to a wireless network between objects, usually the network will be wireless and self-configuring. Internet of Things (IOT) is one of the major component advances in present time that links the internet with everyday sensor and working devices. Smart objects play an important role in the Internet of Things vision, since embedded communication and information technology would have the potential to change the utility of these objects. Using sensors they are able to recognize their condition, and via built-in connecting power they would be able to interact with each other.

Internet of Things (IOT) came into existence in 2009. It encircles the idea of connecting all gadgets and devices to the internet. The concept of Internet of Things is actually trying to change our world by connecting everything with each other. It is basically making our health, and businesses, society by developing products which would lead to a comfortable life. By 2020 it is estimated that, about 50 billion devices would be linked to the Internet and the market would be worth around 14 trillion USD.

IOT in different application domains alike web property of everyday objects may be accustomed remotely confirm their state in order that we will perpetually collect the info and knowledge on physical objects and processes. This qualifies several options of the
important world to be spot at a antecedently unattained level of detail and at terribly low value nearly too negligible. This could not afford an improved understanding of the underlying processes, however additionally for a lot of economical management and management. The potential to react to events during this world in associate automatic manner not solely disclose new opportunities for addressing composite or unfavorable
things, however additionally allows a large type of business processes to be optimized.

\section{Air Pollution}

Air pollution occurs when harmful or excessive quantities of substances are introduced into Earth's atmosphere. Sources of air pollution include gases (such as ammonia, carbon monoxide, sulfur dioxide, nitrous oxides, methane and chlorofluorocarbons), particulates (both organic and inorganic), and biological molecules. It may cause diseases, allergies and even death to humans; it may also cause harm to other living organisms such as animals and food crops, and may damage the natural or built environment. Both human activity and natural processes can generate air pollution.

Air pollution is a significant risk factor for a number of pollution-related diseases, including respiratory infections, heart disease, COPD, stroke and lung cancer. The human health effects of poor air quality are far reaching, but principally affect the body's respiratory system and the cardiovascular system. Individual reactions to air pollutants depend on the type of pollutant a person is exposed to, the degree of exposure, and the individual's health status and genetics. Indoor air pollution and poor urban air quality are listed as two of the world's worst toxic pollution problems in the 2008 Blacksmith Institute World's Worst Polluted Places report. Outdoor air pollution alone causes 2.1 to 4.21 million deaths annually. Overall, air pollution causes the deaths of around 7 million people worldwide each year, and is the world's largest single environmental health risk.



